---
title: "Introduction to StatComp20012"
author: "Ye Peng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20012}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



# Overview

  __StatComp20012__ is a simple R package developed for the conventional interval estimation of data from normal population.firstly,We use a function named _desstat_  to do simple descriptive statistics on the data.Then,We can choose which function to call to estimate the interval according to the purpose.




## Descriptive analysis

  The source R code for _desstat_ is as follows:
```{r}
desstat<- function(x,parametirc=TRUE,print=FALSE) {
  if(parametirc){
    center<-mean(x);spread<-sd(x)
  }else{
    center<- median(x);spread<-mad(x)
  }
  if(print & parametirc){
    cat("Mean=",center,"\n","SD=",spread,"\n")
  }else if(print & !parametirc){
    cat("Median=",center,"\n","MAD=",spread,"\n")
  }
  result<-list(center=center,spread=spread)
  return(result)
}
```

  The _desstat_ is used for descriptive analysis of a set of data. You can choose to output the mean and variance of the data or output the median and absolute deviation of the data.


## Interval estimation

  The following three functions are designed for interval estimation. _mu_ is used for interval estimation of the mean value of normal population,when the population variance is known. _sigma_ is used for interval estimation of the variance of normal population,when the population variance is known. _mux_muy_ is used for interval estimation of the difference between the mean values of two normal population,When the variance of two populations is the same.


### Mean interval estimation of single normal population

```{r}
mu <- function(alpha,x,sigma=NA){
  n <- length(x)
  meanx <- mean(x)
  if(is.na(sigma)){
    t1 <- qt(1-alpha/2,n-1)
    t2 <- qt(1-alpha,n-1)
    mu11 <- meanx - t1*sqrt(sum((x-meanx)^2)/(n-1))/sqrt(n)
    mu12 <- meanx + t1*sqrt(sum((x-meanx)^2)/(n-1))/sqrt(n)
    mu21 <- meanx + t2*sqrt(sum((x-meanx)^2)/(n-1))/sqrt(n)
    mu22 <- meanx - t2*sqrt(sum((x-meanx)^2)/(n-1))/sqrt(n)
  }
  else{
    u1 <- qnorm(1-alpha/2,0,1)
    u2 <- qnorm(1-alpha,0,1)
    mu11 <- meanx - u1*sigma/sqrt(n)
    mu12 <- meanx + u1*sigma/sqrt(n)
    mu21 <- meanx + u2*sigma/sqrt(n)
    mu22 <- meanx - u2*sigma/sqrt(n)
  }
  string1 <- paste('The bilateral confidence interval is:[',mu11,', ',mu12,'].',sep='')
  string2 <- paste('Upper bound of unilateral confidence interval:',mu21,'.',sep='')
  string3 <- paste('Lower bound of one side confidence interval:',mu22,'.',sep='')
  string <- data.frame(Confidence_Interval=c(string1,string2,string3))
  return(string)
}
```

### Variance interval estimation of single normal population

```{r}
sigmA <- function(alpha,x,mu=NA){
  n <- length(x)
  if(is.na(mu)){
    meanx <- mean(x)
    chisq11 <- qchisq(1-alpha/2,n-1)
    chisq12 <- qchisq(alpha/2,n-1)
    chisq21 <- qchisq(alpha,n-1)
    chisq22 <- qchisq(1-alpha,n-1)
    sigma11 <- sqrt(sum((x-meanx)^2)/chisq11)
    sigma12 <- sqrt(sum((x-meanx)^2)/chisq12)
    sigma21 <- sqrt(sum((x-meanx)^2)/chisq21)
    sigma22 <- sqrt(sum((x-meanx)^2)/chisq22)
  }
  else{
    chisq11 <- qchisq(1-alpha/2,n)
    chisq12 <- qchisq(alpha/2,n)
    chisq21 <- qchisq(alpha,n)
    chisq22 <- qchisq(1-alpha,n)
    sigma11 <- sqrt(sum((x-mu)^2)/chisq11)
    sigma12 <- sqrt(sum((x-mu)^2)/chisq12)
    sigma21 <- sqrt(sum((x-mu)^2)/chisq21)
    sigma22 <- sqrt(sum((x-mu)^2)/chisq22)
  }
  string1 <- paste('The bilateral confidence interval is:[',sigma11,', ',sigma12,'].',sep='')
  string2 <- paste('Upper bound of unilateral confidence interval:',sigma21,'.',sep='')
  string3 <- paste('Lower bound of one side confidence interval:',sigma22,'.',sep='')
  string <- data.frame(Confidence_Interval=c(string1,string2,string3))
  return(string)
}
```


### Interval estimation of the difference between the mean values of two normal populations

```{r}
mux_muy <- function(alpha,x,y,sigmax=NA,sigmay=NA){
  if(is.na(sigmax)|is.na(sigmay)){
    meanx <- mean(x)
    meany <- mean(y)
    m <- length(x)
    n <- length(y)
    sx <- sqrt(sum((x-meanx)^2)/(m-1))
    sy <- sqrt(sum((y-meany)^2)/(n-1))
    sw <- sqrt((m-1)*sx^2/(m+n-2)+(n-1)*sy^2/(m+n-2))
    mu11 <- (meanx-meany)+qt(1-alpha/2,m+n-2)*sw*sqrt(1/m+1/n)
    mu12 <- (meanx-meany)-qt(1-alpha/2,m+n-2)*sw*sqrt(1/m+1/n)
  }
  else{
    meanx <- mean(x)
    meany <- mean(y)
    m <- length(x)
    n <- length(y)
    sx <- sqrt(sum((x-meanx)^2)/m)
    sy <- sqrt(sum((y-meany)^2)/n)
    sw <- sqrt((m-1)*sx^2/(m+n-2)+(n-1)*sy^2/(m+n-2))
    mu11 <- (meanx-meany)+qt(1-alpha/2,m+n)*sw*sqrt(1/m+1/n)
    mu12 <- (meanx-meany)-qt(1-alpha/2,m+n)*sw*sqrt(1/m+1/n)
  }
  string1 <- paste('The confidence interval is:[',mu12,', ',mu11,'].',sep='')
  return(string1)
}
```























